---
title: "R Homework"
author: "Connor Ward and Justyn Rivera"
date: "3 April 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r pressure, echo=FALSE}

##Weight and Hindfoot Plots 
library(tidyverse)
download.file("https://ndownloader.figshare.com/files/2292169",
              "data/portal_data_joined.csv")
surveys <- read_csv("data/portal_data_joined.csv")

surveys_complete <- surveys %>%
  filter(!is.na(weight), !is.na(hindfoot_length), !is.na(sex),
         species_id != "")
## Weight 
ggplot(surveys_complete, aes(x=species_id, y = weight)) +
  geom_jitter(alpha = .1,color = "green") + geom_boxplot(alpha =.5)
## Hindfoot Length
ggplot(surveys_complete, aes(x=species_id, y = hindfoot_length)) +
  geom_jitter(alpha = .1,color = "red") + geom_boxplot(alpha =.5)
```
  The first graph shows the average weights of each species where the second shows respective average hindfoot lengths. Comparing the two, there seems to be a small relationships between the weight and foot length. We attribute this to the relatively obvious notion that with greater mass comes greater "structures" to support the species' individuals. However, the data doesnt show all hindfoot lengths and even less individual weight values that skew the data in terms of making conclusive comparisons.