---
title: "R Homework"
author: "Connor Ward and Justyn Rivera"
date: "3 April 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r pressure, echo=FALSE}

library(tidyverse)
library(gridExtra)
download.file("https://ndownloader.figshare.com/files/2292169",
              "data/portal_data_joined.csv")
surveys <- read.csv("data/portal_data_joined.csv")

surveys_complete <- surveys %>%
  filter(!is.na(weight), !is.na(hindfoot_length), !is.na(sex),
         species_id != "")

weightplot <- ggplot(surveys_complete, aes(x=species_id, y = weight)) +
  geom_jitter(alpha = .1,color = "blue") + geom_boxplot(alpha =.5) +
  xlab("Species ID")+ylab("Weight (kg)")

lengthplot <- ggplot(surveys_complete, aes(x=species_id, y = hindfoot_length)) +
  geom_jitter(alpha = .1,color = "red") + geom_boxplot(alpha =.5) +
  xlab("Species ID")+
  ylab("Hindfoot Length (cm)")

grid.arrange(weightplot,lengthplot)

#need to do r-squared and p-values
ggplot(surveys_complete, aes(x=weight, y = hindfoot_length)) +
  geom_point(alpha = .05,color = "blue") + xlab("Weight (kg)")+
  ylab("Hindfoot Length (cm)")

mean_wl <- surveys_complete %>% group_by(species_id) %>%
  summarize(mean_length = mean(hindfoot_length),
            mean_weight = mean(weight))

#need to do r-squared and p-values
ggplot(mean_wl, aes(x=mean_weight, y=mean_length, color=species_id))+
  geom_point()+xlab("Mean Weight (kg)")+ylab("Mean Hindfoot Length (cm)")
```
  With the surveys data set, we created four plots to visualize relationships of given species between weight and hindfoot length.The first contained weights compared to each species where the second shows respective average hindfoot lengths. Comparing the two, there seems to be a small relationships between the weight and foot length. We attribute this to the relatively obvious notion that with greater mass comes greater "structures" to support the species' individuals. However,there are few intuative interpetations of the first two due to the the data having gaps. There are missing entries for hindfoot lengths and even more left out individual weight values. This skewed the data in terms of making conclusive comparisons. Be that as it may, looking at the third graph, which actually plots the weights agains the hindfoot lenghts our initial interpitation was relatively validated. Moving along the X-Axis, as weight values grow it would seem that there is a parallel growth in hindfoot lenghts. With that being said, some of the larger weight values dont show equally high hindfoot lengths but we attribute this to the potential of an individual to continually gain weight but whose "structures"(i.e hindfootlengths) stop growing after reaching a certain point(maturity). Lastly, the final graph takes the mean values of both weight and hindfoot length, plots them against eachother again, and results in an even more validating graph. Here, a gradual curve can be seen where as average weights of all individuals in each species grow so do the average hindfoot lengths. In total, the results we found were that there is a coorelation for increasing weight and respective hindfoot lengths but more data/variables are needed to create actual conclusive interpretations. Also, the data that is missing if present, would help our data be more accurate. 