---
title: "R Homework"
author: "Connor Ward and Justyn Rivera"
date: "3 April 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r pressure, echo=FALSE}

library(tidyverse)
library(gridExtra)
download.file("https://ndownloader.figshare.com/files/2292169",
              "data/portal_data_joined.csv")
surveys <- read.csv("data/portal_data_joined.csv")

surveys_complete <- surveys %>%
  filter(!is.na(weight), !is.na(hindfoot_length), !is.na(sex),
         species_id != "")

weightplot <- ggplot(surveys_complete, aes(x=species_id, y = weight)) +
  geom_jitter(alpha = .1,color = "blue") + geom_boxplot(alpha =.5) +
  xlab("Species ID")+ylab("Weight (kg)")

lengthplot <- ggplot(surveys_complete, aes(x=species_id, y = hindfoot_length)) +
  geom_jitter(alpha = .1,color = "red") + geom_boxplot(alpha =.5) +
  xlab("Species ID")+
  ylab("Hindfoot Length (cm)")

grid.arrange(weightplot,lengthplot)

#need to do r-squared and p-values
ggplot(surveys_complete, aes(x=weight, y = hindfoot_length)) +
  geom_point(alpha = .05,color = "blue") + xlab("Weight (kg)")+
  ylab("Hindfoot Length (cm)")

mean_wl <- surveys_complete %>% group_by(species_id) %>%
  summarize(mean_length = mean(hindfoot_length),
            mean_weight = mean(weight))

#need to do r-squared and p-values
ggplot(mean_wl, aes(x=mean_weight, y=mean_length, color=species_id))+
  geom_point()+xlab("Mean Weight (kg)")+ylab("Mean Hindfoot Length (cm)")
```
  The first graph shows the average weights of each species where the second shows respective average hindfoot lengths. Comparing the two, there seems to be a small relationships between the weight and foot length. We attribute this to the relatively obvious notion that with greater mass comes greater "structures" to support the species' individuals. However, the data doesnt show all hindfoot lengths and even less individual weight values that skew the data in terms of making conclusive comparisons.